### 2007-01-03 Documentation/part2.tex
Corrected the description of the cross section files
Part of manual updated

\index{aedl}{inlcude@{\tt include}}
As another feature of AEDL one can use include files with the {\tt include} command. Includes can be nested up to {\tt MAX\_INCLUSION\_DEPTH}, which is currently set to $10$. Error reporting works 
 for nested includes, too. The included file is not required to begin 
 with {\tt \%!GLoBES} to facilitate cut and paste:
\begin{quote}
{\tt include "./file\_1"}
\end{quote}
With this include mechanism, one can use constructions such as 
\begin{quote}
{\tt    include  "NuFact.gls"\\
        \#NEXT\#\\
        include   "JHFHK.gls"
}
\end{quote}
in order to initialize a combined analysis of the experiments defined in the files {\tt NuFact.gls} and {\tt JHFHK.gls}. Note that one has 
to use quotation marks for filenames in \AEDL.\index{norm}{File names}
Even if one uses the
automatic variable {\tt \#CC} in both experiments, 
but the cross section data are different (for example, because of different target nuclei), the correct 
cross section data will be applied to each of the experiments. 
Note that, alternatively, one can 
also load both files successively by two separate calls of 
\GLB{InitExperiment}.

@@

Cross sections are in \GLOBES\ given as differential cross section per energy:
\begin{equation}
\hat\sigma(E)=\sigma(E)/E\,\left[ 10^{-38}\,
\frac{\mathrm{cm}^2}{\mathrm{GeV}^2} \right]
\end{equation}
The software assumes that the cross section files are text files with 
seven columns and $1001$ lines of the form
\index{norm}{Cross section!file}
\index{aedl}{{\tt cross}!cross file@{\tt  "@cross\_file}}
\begin{quotation}
$\mathrm{log}_{10} E\quad
\hat\sigma_{\nu_e}\quad
\hat\sigma_{\nu_\mu}\quad
\hat\sigma_{\nu_\tau}\quad
\hat\sigma_{\bar\nu_e}\quad
\hat\sigma_{\bar\nu_\mu}\quad
\hat\sigma_{\bar\nu_\tau}$
\end{quotation}
Here the logarithms of the energy values have to be equidistant. For 
arbitrary energies, linear interpolation is used. If the energy leaves the
range of values given in the file, $0.0$ will be assumed. In general, it is advisable to provide the cross sections in the range between {\tt \$sampling\_min} and {\tt \$sampling\_max} (\cf, \Sec~\ref{sec:energy}).
Unused cross sections have to be filled with zeros, and can not
 be just omitted.

>>>>

\index{aedl}{include@{\tt include}}
As another feature of AEDL one can use include files with the {\tt include} command. Includes can be nested up to {\tt MAX\_INCLUSION\_DEPTH}, which is currently set to $10$. Error reporting works 
 for nested includes, too. The included file is not required to begin 
 with {\tt \%!GLoBES} to facilitate cut and paste:
\begin{quote}
{\tt include "./file\_1"}
\end{quote}
With this include mechanism, one can use constructions such as 
\begin{quote}
{\tt    include  "NuFact.gls"\\
        \#NEXT\#\\
        include   "JHFHK.gls"
}
\end{quote}
in order to initialize a combined analysis of the experiments defined in the files {\tt NuFact.gls} and {\tt JHFHK.gls}. Note that one has 
to use quotation marks for filenames in \AEDL.\index{norm}{File names}
Even if one uses the
automatic variable {\tt \#CC} in both experiments, 
but the cross section data are different (for example, because of different target nuclei), the correct 
cross section data will be applied to each of the experiments. 
Note that, alternatively, one can 
also load both files successively by two separate calls of 
\GLB{InitExperiment}.

@@

Cross sections in \GLOBES\ are given as total cross section divided by energy:
\begin{equation}
\hat\sigma(E)=\sigma(E)/E\,\left[ 10^{-38}\,
\frac{\mathrm{cm}^2}{\mathrm{GeV}} \right]
\end{equation}
The software assumes that the cross section files are text files with 
seven columns and $1001$ lines of the form
\index{norm}{Cross section!file}
\index{aedl}{{\tt cross}!cross file@{\tt  "@cross\_file}}
\begin{quotation}
$\mathrm{log}_{10} E\quad
\hat\sigma_{\nu_e}\quad
\hat\sigma_{\nu_\mu}\quad
\hat\sigma_{\nu_\tau}\quad
\hat\sigma_{\bar\nu_e}\quad
\hat\sigma_{\bar\nu_\mu}\quad
\hat\sigma_{\bar\nu_\tau}$
\end{quotation}
Here the logarithms of the energy values have to be equidistant. For 
arbitrary energies, linear interpolation is used. If the energy leaves the
range of values given in the file, $0.0$ will be assumed. In general, it is advisable to provide the cross sections in the range between {\tt \$sampling\_min} and {\tt \$sampling\_max} (\cf, \Sec~\ref{sec:energy}).
Unused cross sections have to be filled with zeros, and can not
 be just omitted.
